An SMT-based Approach to Coverability Analysis

### 2014-02-05 paper/workspace/main.tex
Separated figure lamport network.
Added results for methods safety and safety by refinement

@@

\begin{center}
  \includegraphics[width=10cm]{lamport}
\end{center}

@@

    a     = 1 + t1 - t2
    ^       ^   ^    ^
    |       |   |    |
    |       |   |    |
    |       |   |    |
    |       |   |   # of tokens taken from a
    |       |   |    
    |       |  # of tokens given to a
    |       |
    |      initial number of tokens in a
    |
    number of tokens in a

    b     = 0 - t1 + t2
    nbit2 = 0

@@

    a     >= 0
    b     >= 0
    nbit2 >= 0

@@

    a + b >= 2
\end{verbatim}

@@

  - Property P:

    b = 0

    b >= 1

  - Assignment A:
    a     = 0
    b     = 1
    nbit2 = 0
    t1    = 0
    t2    = 1

@@

    - Trap implications:
               t2
             ----------
    a     => b \/ nbit2
    ^           ^      ^
    |           |      |
    |           |     nbit2 \in S
    |           |
    |          b \in S
    |
    a \in S

    nbit2 => b \/ nbit2
    b     => a

    - At least one of the initially marked places belongs to S:
    a

    - None of the marked places in A belongs to S:
    ~b

  - Assignment A_\theta:
    a     = true
    b     = false
    nbit2 = true

  - Refinement constraint \delta:
    a + b >= 1
    ^   ^
    |   |
    -----
      |
      S = {a, b}, therefore \delta excludes assignment A in the next iteration
\end{verbatim}

>>>>

  - Property: p3 + q5 <= 1

@@

\input{fig_lamport_net}

@@

    p1    = 1 - s1      + s3
    ^       ^   ^         ^
    |       |   |         |
    |       |   |         |
    |       |   |         |
    |       |   |        # of tokens given to p1
    |       |   |    
    |       |  # of tokens taken from p1
    |       |
    |      initial number of tokens in p1
    |
    number of tokens in p1

    p2    = 0 + s1 - s2
    p3    = 0      + s2 - s3
    bit1  = 0 + s1      - s3
    nbit1 = 1 - s1      + s3
    q1    = 1 +              - t1           + t4      + t6
    q2    = 0 +              + t1 - t2           - t5
    q3    = 0 +                   + t2 - t3
    q4    = 0 +                        + t3 - t4
    q5    = 0 +                                  + t5 - t6
    nbit2 = 1 +              - t1      + t3           + t6

@@

    p1    >= 0
    p2    >= 0
    p3    >= 0
    bit1  >= 0
    nbit1 >= 0
    q1    >= 0
    q2    >= 0
    q3    >= 0
    q4    >= 0
    q5    >= 0
    nbit2 >= 0

@@

    p3 + q5 >= 2
\end{verbatim}

@@

  - Assignment A:
    p1    = 0
    p2    = 0
    p3    = 1
    bit1  = 1
    nbit1 = 0
    q1    = 0
    q2    = 0
    q3    = 0
    q4    = 0
    q5    = 0
    nbit2 = 0

@@

    - Trap implications:
                s1
             ----------
    p1    => p2 \/ bit1
    ^           ^      ^
    |           |      |
    |           |     bit1 \in S
    |           |
    |          p2 \in S
    |
    p1 \in S

    p2    => p3 \/ nbit2
    p3    => p1 \/ nbit1
    bit1  => (p1 \/ nbit1) /\ (q3 \/ bit1)
    nbit1 => (p2 \/ bit1) /\ (q1 \/ nbit1) /\ (q5 \/ nbit1)
    q1    => q2
    q2    => (q3 \/ bit1) /\ (q5 \/ nbit1)
    q3    => q4 \/ nbit2
    q4    => q1 \/ nbit1
    q5    => q1 \/ nbit2
    nbit2 => q2 /\ (p3 \/ nbit2)

    - At least one of the initially marked places belongs to S:
    p1 \/ q1 \/ nbit1 \/ nbit2

    - None of the marked places in A belongs to S:
    ~p3 /\ ~q5 /\ ~bit1

  - Assignment A_\theta:
    p1    = false
    p2    = true
    p3    = false
    bit1  = false
    nbit1 = true
    q1    = false
    q2    = true
    q3    = true
    q4    = false
    q5    = false
    nbit2 = true

  - Refinement constraint \delta:
    p2 + q3 + q5 + nbit1 + nbit2 >= 1
    ^    ^    ^    ^       ^
    |    |    |    |       |
    ------------------------
      |
      S = {p2, q3, q5, nbit1, nbit2}, therefore \delta excludes
      assignment A in the next iteration
\end{verbatim}
